---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# doclisting

<!-- badges: start -->
<!-- badges: end -->

doclisting automatically generates itemized lists of methods for a generic function, suitable for inclusion in roxygen2 documentation. Each method links to its help topic, and methods from other packages are clearly labeled.

## Installation

You can install the development version of doclisting from GitHub:

``` r
pak::pak("hadley/doclisting")
```

## Usage

`methods_list()` generates Rd markup listing all methods for a generic:

```{r}
library(doclisting)
cat(methods_list("mean"))
```

You can use it in roxygen2 documentation in two ways:

*   Compute methods when the package is documented (i.e. at
    `devtools::document()` time), use inline R code in your roxygen
    comment:

        #' @description
        #' `r knitr::inline_expr('doclisting::methods_list("my_generic")')`

    You'll need to add `doclisting` to `Suggests`.

*   Compute methods when documentation is rendered (i.e. at `?` time),
    use an Rd code block:
        
        #' @description
        #' `Rd doclisting::methods_list("my_generic")`

    You'll need to add `doclisting` to `Imports`.
